Analysis of the included studies

### 2023-04-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Moved up the setup chunk

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('ggthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
library('ggwordcloud')

@@

#directories
# Figures
figs_dir <- "../figs_manuscript"

>>>>

```{r}
#' load packages
library('tidyverse')
library('ggthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
library('ggwordcloud')

@@

```{r}
#directories
# Figures
figs_dir <- "../figs_manuscript"
